A VIRTUAL RESEARCH ENVIRONMENT TO DOCUMENT AND ANALYZE NON-ALPHABETIC WRITING SYSTEMS. A Case Study for Maya Writing.

### 2015-12-16 source/8/EAGLE_2016_submission_8_revised.tex
added bst files in each folder, started work on bibliography through Zotero, added CNR paper

\subsection[Registering Object Data ]{Registering Object Data}
\noindent When designing the digital epigraphic work environment, one must also account for the current state of decipherment of
the script and language that are to be documented. Thus, Classic Mayan presents great challenges, as at least one third
of the known graphemes have not yet been completely deciphered. Even when a lexeme can be read, its etymology or
semantic domain is often unknown, and in some cases not even its lexical class can be determined, which causes
difficulties when attempting to read and understand a text. In order to decode an unknown sign, word, or sign sequence
in its respective context of use, for instance, semantic fields are generally investigated by means of applied
substitution. From a structuralist perspective, this method investigates the paradigmatic relation between two
linguistic entities as indicated by whether or not they appear in the same context \citep{Bußmann2002}. This step yields
results when sufficient quantities of data can be digitally compiled, marked up and investigated using corpus
linguistics.

@@

Thus, when creating a standard for non-alphabetic scripts, object metadata and annotations for orthographic and
linguistic analysis must be taken into account, and the creative process should also promote discussion of
terminological and typographic conventions for these annotations \citep{SachseDürr2015}. The goal is to create a generic
markup model that can be implemented regardless of the particular script or language in question. The inscriptions of
the Maya hieroglyphic writing system alone feature attestations of various vernacular languages \citep{LacadenaWichmann2002}, a phenomenon which raises several preliminary questions: what exactly are the demands, and what are the goals of
an epigraphic and linguistic annotation? Where do possibilities and limitations exist for annotating these writing
systems using established standards, such as TEI or EpiDoc? Existing standards have to be modified to some extend and
possibly new standards have to be created, to overcome these limitations.

\subsubsection[Representing the Primary Text Source]{Representing the Primary Text Source}
When defining a text, acknowledging an interpretation of the source text itself is unavoidable. The meaning of the
``original text'' that resides in the ``source text'' is an important point of discussion in epigraphy. Thus, the
annotation does not contain a guiding text in the conventional sense, because it is merely reconstructed using all
given text information and one’s own conclusions and interpretations, and then represented with the aid of alphabetic
transliteration and transcription. In this respect, one should always leave open the possibility of separating primary
data (in the case of hieroglyphic texts, photographs of the text carriers, for example) and secondary data (e.g.
drawings or interpretive annotations) \citep{Stührenberg2012}. This strategy can be implemented using stand-off annotations
for data. Similarly, such an annotation should permit multiple descriptions, i.e. alternative statements concerning the
data \citep{Stührenberg2012}. For example, sign sequences in Classic Mayan can be variously analyzed depending in a
particular vernacular context \citep{Gronemeyer2014}. Only in this manner can various ways of thinking be appropriately
recorded and relayed to the scientific community for discussion.

@@

\subsubsection[Graphetics ]{Graphetics }
Graphetics concerns the formal structure of linguistic units and the structure of texts \citep{Crystal1997}. Classic Maya
hieroglyphic inscriptions, for instance, may display a very high degree of variation in writing styles for arranging
texts, a phenomenon which is deserving of investigation. In this manner, various systems of notation are studied in
their individual, social, and typographic aspects, for instance \citep{Bußmann2002}. Similarly, in paleography, script
decipherment is examined from graphetic perspective \citep{Bußmann2002}. The arrangement of texts, for instance, different
grapheme or block sizes of text fields, or different styles of hieroglyphic writing (equivalent to alphabetic font
style and size) are analyzed.

@@

\subsubsection{Graphemics }
When analyzing the contents of these texts, it is important to investigate meaningful variation underlying the manner in
which the writing is arranged and to thereby identify distinct units \citep{Bußmann2002}. Graphemics is devoted to this area
of research, and consequently to exploring the meaningfully distinct features of signs.

>>>>

\subsection[Registering Object Data ]{Registering Object Data}
\noindent When designing the digital epigraphic work environment, one must also account for the current state of decipherment of
the script and language that are to be documented. Thus, Classic Mayan presents great challenges, as at least one third
of the known graphemes have not yet been completely deciphered. Even when a lexeme can be read, its etymology or
semantic domain is often unknown, and in some cases not even its lexical class can be determined, which causes
difficulties when attempting to read and understand a text. In order to decode an unknown sign, word, or sign sequence
in its respective context of use, for instance, semantic fields are generally investigated by means of applied
substitution. From a structuralist perspective, this method investigates the paradigmatic relation between two
linguistic entities as indicated by whether or not they appear in the same context \citep{Bussmann2002}. This step yields
results when sufficient quantities of data can be digitally compiled, marked up and investigated using corpus
linguistics.

@@

Thus, when creating a standard for non-alphabetic scripts, object metadata and annotations for orthographic and
linguistic analysis must be taken into account, and the creative process should also promote discussion of
terminological and typographic conventions for these annotations \citep{SachseDurr2015}. The goal is to create a generic
markup model that can be implemented regardless of the particular script or language in question. The inscriptions of
the Maya hieroglyphic writing system alone feature attestations of various vernacular languages \citep{LacadenaWichmann2002}, a phenomenon which raises several preliminary questions: what exactly are the demands, and what are the goals of
an epigraphic and linguistic annotation? Where do possibilities and limitations exist for annotating these writing
systems using established standards, such as TEI or EpiDoc? Existing standards have to be modified to some extend and
possibly new standards have to be created, to overcome these limitations.

\subsubsection[Representing the Primary Text Source]{Representing the Primary Text Source}
When defining a text, acknowledging an interpretation of the source text itself is unavoidable. The meaning of the
``original text'' that resides in the ``source text'' is an important point of discussion in epigraphy. Thus, the
annotation does not contain a guiding text in the conventional sense, because it is merely reconstructed using all
given text information and one’s own conclusions and interpretations, and then represented with the aid of alphabetic
transliteration and transcription. In this respect, one should always leave open the possibility of separating primary
data (in the case of hieroglyphic texts, photographs of the text carriers, for example) and secondary data (e.g.
drawings or interpretive annotations) \citep{Stuhrenberg2012}. This strategy can be implemented using stand-off annotations
for data. Similarly, such an annotation should permit multiple descriptions, i.e. alternative statements concerning the
data \citep{Stuhrenberg2012}. For example, sign sequences in Classic Mayan can be variously analyzed depending in a
particular vernacular context \citep{Gronemeyer2014}. Only in this manner can various ways of thinking be appropriately
recorded and relayed to the scientific community for discussion.

@@

\subsubsection[Graphetics ]{Graphetics }
Graphetics concerns the formal structure of linguistic units and the structure of texts \citep{Crystal1997}. Classic Maya
hieroglyphic inscriptions, for instance, may display a very high degree of variation in writing styles for arranging
texts, a phenomenon which is deserving of investigation. In this manner, various systems of notation are studied in
their individual, social, and typographic aspects, for instance \citep{Bussmann2002}. Similarly, in paleography, script
decipherment is examined from graphetic perspective \citep{Bussmann2002}. The arrangement of texts, for instance, different
grapheme or block sizes of text fields, or different styles of hieroglyphic writing (equivalent to alphabetic font
style and size) are analyzed.

@@

\subsubsection{Graphemics }
When analyzing the contents of these texts, it is important to investigate meaningful variation underlying the manner in
which the writing is arranged and to thereby identify distinct units \citep{Bussmann2002}. Graphemics is devoted to this area
of research, and consequently to exploring the meaningfully distinct features of signs.
